---
output: github_document
always_allow_html: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# R.COVID.19

<!-- badges: start -->
<!-- [![Travis build status](https://travis-ci.org/Fredo-XVII/R.COVID.19.svg?branch=master)](https://travis-ci.org/Fredo-XVII/R.COVID.19) -->
<!-- badges: end -->

The goal of R.COVID.19 is to simply aquire data for the disease COVID 19 from sources that make readily available. No promises are made to the validaty of the data as their are many people at the sources working on that. Because these functions link to the sources, the data should update as the sources update. If data is not being generated, please open an issue so that I can look into the broken link.  The sources for the data is listed below.

## Installation

You can install the released version of R.COVID.19 from [CRAN](https://CRAN.R-project.org) with: (NOT YET ON CRAN)

``` r
#install.packages("R.COVID.19")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
# devtools::install_github("Fredo-XVII/R.COVID.19")
```
## Examples

This is a basic example which shows you how to solve a common problem:

```{r libraries}
library(R.COVID.19)
library(tidyverse)
```


### John Hopkins University Data
source: [GITHUB](https://github.com/CSSEGISandData/COVID-19)
table: csse_covid_19_time_series
```{r John_Hopkins_Data}
confirmed <- R.COVID.19::covid19_confirmed()

deaths <- R.COVID.19::covid19_deaths()

combo <- confirmed %>% left_join(deaths) %>% 
  dplyr::mutate(mortality_rate = round((.$deaths_cases / .$confirmed_cases)*100,2))

knitr::kable(combo %>% filter(`Country/Region` == "US") %>% tail(10), format = "html") %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped"))
```


### Data from The New York Times, based on reports from state and local health agencies.
source: [GITHUB](https://github.com/nytimes/covid-19-data)
```{r NY_Times_Data}
us_co_cases <- R.COVID.19::covid19_us_co() %>% 
  dplyr::mutate(mortality_rate = round((.$deaths / .$cases)*100,2))
knitr::kable(us_co_cases %>% filter(state == "New York") %>% tail(10), format = "html") %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")
```

